\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-19 chapters/5_experiments_compare_rules.tex
Finish polishing intro, abstract, conclusions

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
DTWS + \algname{} & Average& \TODO{} \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores achieved by Different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs}}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

\subsection{CREMI Challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by \TODO{\algname{}} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

>>>>

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
DTWS + \algname{} & Average& \TODO{} \\
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs}}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

\subsection{Data: CREMI Challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from a serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by \algname{} (WSDT+\algname{}) or approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

### 2019-05-19 chapters/5_experiments_noise.tex
Finish polishing intro, abstract, conclusions

\textbf{Sum linkage } 
% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. 
All our experiments, as well as the examples in Fig. \ref{fig:cremi_comparison}, show that \algname{} with \emph{Sum} linkage is the algorithm with the highest probability of under-clustering and incorrectly merging segments. This is strongly related to the  empirical observation highlighted in Fig. \ref{fig:intro_figure}, where it is shown that the agglomeration order given by \algname{} with \emph{Sum} linkage is clearly different as compared to those given by other linkage criteria like \emph{Average} or \emph{Abs Max}. Particularly, a \emph{Sum} statistic tends to grow clusters one after the other. The intuitive explanation behind this is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, other linkage criteria grow clusters of similar sizes in parallel and accumulate more valuable statistics between the clusters.

>>>>

\textbf{Sum linkage } 
% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. 
All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig. \ref{fig:cremi_comparison} for an example). This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig. \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic. An intuitive explanation of this fact is the following: initially, most of the infra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, as we also see in Fig. \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.

### 2019-05-19 chapters/6_conclusions.tex
Finish polishing intro, abstract, conclusions

% !TEX root = ../agglo_clust_review.tex
\section{Conclusions}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Conclusion}
We have presented a novel theoretical framework for agglomerative clustering of graphs with both positive and negative weights and we have shown that several existing clustering algorithms, like the Mutex Watershed, can be reformulated as special cases of one underlying agglomerative algorithm. This framework also allowed us to introduce new algorithms, one of which (based on an average linkage) outperformed all the others and proved to be a simple and remarkably robust approach to process short- and long-range predictions of a CNN applied to an instance segmentation task.
On biological images, this simple average agglomeration algorithm can represent a valuable choice for an user that is not willing to spend a lot of time tuning complex task-dependent pipelines. % or test several dataset-dependent

In future work we plan to extend the comparison to other types of graphs and explore common theoretical properties of the algorithms included in the framework.
% We presented a generalized framework and showed how one of the new algorithms included in it, \algname{} with average linkage, represent a simple agglomerative method that does not require the user to tune parameters or generate superpixels and showed extremely competitive performances in biological images, even on the challenging and competitive task of neuron segmentation. (good-quality superpixels are strongly dataset-dependent)
% Compared to previously proposed agglomerative clustering methods for signed graphs, it proved to be the one making best use of the long-range predictions of the CNN; the fact that average is superior to abs max is not surprising, given the literature about HAC with single and average linkage (due to the greediness of the maximum linkage); and enforcing cannot-link constraints, we have also seen that introducing too many long-range mainly repulsive predictions can cause strong over-clustering; tendency to under-clustering of the sum linkage can be explained with the chain-reaction effect and its tendency to grow one cluster at the time that does not allow to build good statistics between adjacent clusters. This is partially fixed by constraints, but not really...
